---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# homework6

<!-- badges: start -->
<!-- badges: end -->

The **homework6** package implements an S4 class `sparse_numeric` for sparse
numeric vectors, where most elements are zero. Only the non-zero values and
their positions are stored.

The package provides:

- Coercion between base `numeric` and `sparse_numeric`
- Arithmetic on sparse vectors:
  - `sparse_add()`, `sparse_sub()`, `sparse_mult()`, `sparse_div()`,
    `sparse_crossprod()`
  - Operator overloads: `+`, `-`, `*`, `/` for `sparse_numeric`
- A `plot()` method to visualize overlapping non-zero entries
- Statistical methods for sparse vectors:
  - `mean()` (including zeros)
  - `norm()` (Euclidean norm)
  - `standardize()` (center and scale)

## Installation

You can install the development version of homework6 like so:

``` r
# from the package root directory
devtools::install()
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(homework6)
## basic example code
x <- as(c(0, 1, 0, 3), "sparse_numeric")
y <- as(c(2, 0, 4, -1), "sparse_numeric")

x + y            # sparse addition
mean(x)          # mean including zeros
norm(x)          # Euclidean norm
z <- standardize(x)
plot(x, y) 
```

